---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gwasforest

<!-- badges: start -->
<!-- badges: end -->

The goal of gwasforest is to extract and reform data from GWAS results, and then make a single integrated forest plot containing multiple windows of which each shows the result of individual SNPs (or other items of interest).

## Installation

You can install the development version of gwasforest from github with:

``` r
devtools::install_github("yilixu/gwasforest", ref = "main")
```

## Example

### customFilename in dataframe format (with standardized column names)

```{r example_01}
library(gwasforest)

tempValue = runif(n = 18, min = 0.01, max = 2)
tempStdErr = tempValue / rep(3:5, times = 6)
eg_customFilename = data.frame(paste0("Marker", 1:6), tempValue[1:6], tempStdErr[1:6], tempValue[7:12], tempStdErr[7:12], tempValue[13:18], tempStdErr[13:18], stringsAsFactors = FALSE)
colnames(eg_customFilename) = c("MarkerName", paste0(rep("Study", times = 6), rep(1:3, each = 2), rep(c("__Value", "__StdErr"), times = 3)))
rm(tempValue, tempStdErr)
```

```{r example_01_cont}
eg_returnList = gwasforest(eg_customFilename, stdColnames = TRUE, valueFormat = "Effect", metaStudy = "Study1", colorMode = "duo")
```

### customFilename in dataframe format (without standardized column names), with customFilename_studyName provided in dataframe format
```{r example_02}
tempValue = runif(n = 18, min = 0.01, max = 2)
tempStdErr = tempValue / rep(3:5, times = 6)
eg_customFilename = data.frame(paste0("Marker", 1:6), tempValue[1:6], tempStdErr[1:6], tempValue[7:12], tempStdErr[7:12], tempValue[13:18], tempStdErr[13:18], stringsAsFactors = FALSE)
colnames(eg_customFilename) = c("MarkerName", paste0(rep("Study", times = 6), rep(1:3, each = 2), sample(LETTERS, 6)))
rm(tempValue, tempStdErr)
eg_customFilename_studyName = data.frame("studyName" = paste0("Study", 1:3), stringsAsFactors = FALSE)
```

```{r example_02_cont}
eg_returnList = gwasforest(eg_customFilename, customFilename_studyName = eg_customFilename_studyName, stdColnames = FALSE, customColnames = c("Value", "StdErr"), valueFormat = "Effect", metaStudy = "Study1", colorMode = "duo")
```

### customFilename_results in dataframe format (run either of the two examples above to see the example results)
```{r example_03}
eg_customFilename_results = eg_returnList[[1]]
```

```{r example plot, echo = TRUE}
library(ggplot2)
 
plot(eg_returnList[[2]])
```
